Variable Selection

### 2015-07-30 cluster.rmd
not sure

all7d<- all7c %>% select(mlsto, inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos, return.pdol, cost.mlsto, hrs.mlsto, balance.mlsto)
all7d$mlsto<- as.character(all7d$mlsto)

@@

>>>>

all7d<- all7c %>% select(mlsto, Year, inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos, return.pdol, cost.mlsto, hrs.mlsto, balance.mlsto)
all7d$mlsto<- as.character(all7d$mlsto)

@@

head(all7d)

### 2015-07-30 var_select.rmd
knn
not sure

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')

@@

#impute Biz.size to be 'local' by default - this is most popular category
all7b[is.na(all7b$Biz.size),]$Biz.size <- 'local'
#impute Biz.type to be 'private' by default - this is most popular category
#client which is 'department of national parks' shall be 'gov'
all7b[is.na(all7b$Biz.type),]$Biz.type <- 'private'
all7b[all7b$code.client %in% 'C2503',]$Biz.type <- 'gov'
#delete charge.ph and charge.pc, Start.Date and End.Date
all7b<- all7b %>% select(-charge.ph, -charge.pc, -Start.Date, -End.Date)
#impute NA no.users as 2 = median and mode
all7b[is.na(all7b$no.users),]$no.users <- 2
#impute NA num.disc as 1 - overwhelmingly the most common
all7b[is.na(all7b$Num.disc),]$Num.disc <- 1
#num.inv and mean.inv both have a single NA value
# this consisted of single large -ve invoice. I think we should delete this case 
all7b<- all7b %>% filter(!is.na(num.inv))
# 7 NA cases with significant dis.sc.mlsto - ie done by contractor 
pc<- c('pc.contracttech','pc.director', 'pc.midtech', 'pc.midpro', 'pc.gradpro', 'pc.seniortech', 'pc.seniorpro', 'pc.pro', 'pc.tech')

@@

# write.csv(all7b,'all7b.csv')

@@

```{r, echo=FALSE}
#read csv file with all the client details - want to merge this with client df
details<- read.csv('17marchclients.csv',
                   na.strings = c("", " ", "NA"))
head(details)
#delete client.contact, client.count, and contact.count columns
details<- details[,c(1,5:9)]
#rename columns
names(details)[2]<- 'Business'
names(details)[4]<- 'Biz.size'
names(details)[5]<- 'Biz.type'
names(details)[6]<- 'Biz.age'

#delete rows with 4 NA values
details<-details[rowSums(is.na(details))!=5,]
details<-details[rowSums(is.na(details))!=4,]

#add row for client code
code.client<- read.csv('code_client2.csv')[,-1]
details<- merge(details, code.client, by.x ='client', by.y ='client2', all.x=TRUE, all.y=FALSE)
details<- transform(details, client.age = 2014- Biz.age)

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)

# write.csv(all7b, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

# write.csv(all7c, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

First need to change code.client and code.contact. Need to assign NA to any code.client or code.contact with less than 3 counts

@@

#all code.clients with counts less than 3 shall be 'NA'
client.check<- ddply(all7c,.(code.client), nrow)
all7c<- merge(all7c, client.check, by='code.client', all.x=TRUE)
all7c$code.client<- as.character(all7c$code.client)
all7c$code.client<- ifelse(all7c$V1>2, all7c$code.client, NA)
all7c$code.client<- as.factor(all7c$code.client)
all7c<- all7c %>% select(-V1)

#all code.contacts with counts less than 3 shall be 'NA'
#code for 'unknown' which should be NA
all7c[all7c$code.contact %in% 'CN1983',]$code.contact <- NA
contact.check<- ddply(all7c,.(code.contact), nrow)
contact.check<- contact.check %>% filter(V1>2)
all7c$code.contact<- as.character(all7c$code.contact)
all7c$code.contact<- ifelse(all7c$code.contact %in% contact.check$code.contact, all7c$code.contact,
                            NA)
all7c$code.contact<- as.factor(all7c$code.contact)

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('RColorBrewer',lib='C:/Progra~1/R/R-3.2.1/library')

@@

#impute Biz.size to be 'local' by default - this is most popular category
all7b[is.na(all7b$Biz.size),]$Biz.size <- 'local'
#impute Biz.type to be 'private' by default - this is most popular category
#client which is 'department of national parks' shall be 'gov'
all7b[is.na(all7b$Biz.type),]$Biz.type <- 'private'
all7b[all7b$code.client %in% 'C2503',]$Biz.type <- 'gov'
#delete charge.ph and charge.pc, Start.Date and End.Date
all7b<- all7b %>% select(-charge.ph, -charge.pc, -End.Date)
#impute NA no.users as 2 = median and mode
all7b[is.na(all7b$no.users),]$no.users <- 2
#impute NA num.disc as 1 - overwhelmingly the most common
all7b[is.na(all7b$Num.disc),]$Num.disc <- 1
#num.inv and mean.inv both have a single NA value
# this consisted of single large -ve invoice. I think we should delete this case 
all7b<- all7b %>% filter(!is.na(num.inv))
# 7 NA cases with significant dis.sc.mlsto - ie done by contractor 
pc<- c('pc.contracttech','pc.director', 'pc.midtech', 'pc.midpro', 'pc.gradpro', 'pc.seniortech', 'pc.seniorpro', 'pc.pro', 'pc.tech')

@@

# write.csv(all7b,'all7b.csv')
all7b<- read.csv('all7b.csv')[,-1]

@@

```{r, echo=FALSE}
#read csv file with all the client details - want to merge this with client df
# details<- read.csv('17marchclients.csv',
#                    na.strings = c("", " ", "NA"))
# head(details)
# #delete client.contact, client.count, and contact.count columns
# details<- details[,c(1,5:9)]
# #rename columns
# names(details)[2]<- 'Business'
# names(details)[4]<- 'Biz.size'
# names(details)[5]<- 'Biz.type'
# names(details)[6]<- 'Biz.age'
# 
# #delete rows with 4 NA values
# details<-details[rowSums(is.na(details))!=5,]
# details<-details[rowSums(is.na(details))!=4,]
# 
# #add row for client code
# code.client<- read.csv('code_client2.csv')[,-1]
# details<- merge(details, code.client, by.x ='client', by.y ='client2', all.x=TRUE, all.y=FALSE)
# details<- transform(details, client.age = 2014- Biz.age)
# 
# #merge client.age column of details to all7b by code.client
# all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)

write.csv(all7b, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

# write.csv(all7c, 'all7c.csv')
# all7c<- read.csv('all7c.csv')[,-1]

@@

First need to change code.client and code.contact. Need to assign NA to any code.client or code.contact with less than 2 counts

@@

#all code.clients with counts less than 3 shall be 'NA'
client.check<- ddply(all7c,.(code.client), nrow)
all7c<- merge(all7c, client.check, by='code.client', all.x=TRUE)
all7c$code.client<- as.character(all7c$code.client)
all7c$code.client<- ifelse(all7c$V1>1, all7c$code.client, NA)
all7c$code.client<- as.factor(all7c$code.client)
all7c<- all7c %>% select(-V1)

#all code.contacts with counts less than 3 shall be 'NA'
#code for 'unknown' which should be NA
all7c[all7c$code.contact %in% 'CN1983',]$code.contact <- NA
contact.check<- ddply(all7c,.(code.contact), nrow)
contact.check<- contact.check %>% filter(V1>1)
all7c$code.contact<- as.character(all7c$code.contact)
all7c$code.contact<- ifelse(all7c$code.contact %in% contact.check$code.contact, all7c$code.contact,
                            NA)
all7c$code.contact<- as.factor(all7c$code.contact)
